%A template for the abstract

\begin{center}
{\large \bf Implementation of Bit-Stream based on P2P overlay network}\\
\end{center}
Xiang Wang\\

Department of Computer Science\\
122 Ninghai Road, Nanjing, 210097, Jiangsu Province\\
Master's thesis\\

\begin{center}
{\bf \emph{Abstract}}\\
\end{center}
{\hspace{1cm}There is no doubt that Video-on-Demand \emph{(VoD)} nowadys is one of the most popular Network Applications on the Internet, contributing to a significant portion of the Internet traffic and being a basis usage of \emph{P2P Internet Protocol} emerging services.
However, with current P2P swarming systems were based on Bit-torrent algorithm, so one or much many central tracker servers were necessary to be deployed in the  open Internet. In this half-centralized P2P system, it was hard to avoid \emph{DDoS} attacking. 
A lot of effort has gone into optimizing the distribution of large files and media in BT-liked P2P system, 
little research has been done on enabling Bit-Stream functionality with P2P swarming systems based on \emph{Kademlia} algorithm . The main challenges reside in ensuring
that users can start watching a movie at any point in time, with small start-up times and sustainable playback rates, and can effectively avoid \emph{DDoS} attacking, which will ensure the performance of VoD service.\\
\hspace*{1cm}{}In this work, this paper address the issues of providing Bit-Stream using P2P \emph{kademlia-based} networks and \emph{OGG} decode containner. This paper investigate scheduling techniques, and network coding in particular. 
Using both simulations and a prototype implementation,
{\footnote{\it{I have set up a project with the name of \emph{KadPeer} in code.google} with GPL2 license. 
(\url{http://code.google.com/p/kadpeer/}). Source code can be downloaded freely.}} 
it shows that high-quality VoD is feasible, 
and give guidelines to build play-as-you-download P2P swarming systems with low start-up delays.
%In this work, we build analytical models to capture
%the performance of BitTorrent-like P2P systems in a steady state, in the presence
%of homogeneous and heterogeneous NAT peers. 
I also build analytical models, in order to improve the overall system performance and fairness
ivmetrics considerably. The analytical models have been validated by simulation results,
which also reveal some interesting facts about the coexistence of NAT and public peers
in \emph{Bit-Stream} systems.}
\vspace*{1cm}

%List keywords here
{\bf Key words}:\it{\emph{ Bit-Stream; VOD; P2P; kademlia; OGG}}\\
%{\bf Computing Reviews (2010) Categories and Subject Descriptors:}\\
%List the classes here.\\
%The following is optional

