%Appendixes do not have section numbers, but they are listed in the table 
%of contents:
\section*{Appendix A: OGG Glossary and Abbreviations}
\label{appendixa}
\addcontentsline{toc}{chapter}{Appendix A: OGG Glossary and Abbreviations}

   \hspace{1cm}bos page: The inital page ( beginning of stream) of a logical bitstream 
       which contains information to identify the codec type and other decoding-relevant infomation.

   chaining (or sequential multiplexing): Concatenation of two or more
      complete physical Ogg bitstreams.

   eos page: The final page (end of stream) of a logical bitstream.

   granule position: An increasing position number for a specific
      logical bitstream stored in the page header.  Its meaning is
      dependent on the codec for that logical bitstream and specified in
      a specific media mapping.

   grouping (or concurrent multiplexing): Interleaving of pages of
      several logical bitstreams into one complete physical Ogg
      bitstream under the restriction that all bos pages of all grouped
      logical bitstreams MUST appear before any data pages.

   lacing value: An entry in the segment table of a page header
      representing the size of the related segment.

   logical bitstream: A sequence of bits being the result of an encoded
      media stream.

   media mapping: A specific use of the Ogg encapsulation format
      together with a specific (set of) codec(s).

   (Ogg) packet: A subpart of a logical bitstream that is created by the
      encoder for that bitstream and represents a meaningful entity for
      the encoder, but only a sequence of bits to the Ogg encapsulation.

   (Ogg) page: A physical bitstream consists of a sequence of Ogg pages
      containing data of one logical bitstream only.  It usually
      contains a group of contiguous segments of one packet only, but
      sometimes packets are too large and need to be split over several
      pages.

   physical (Ogg) bitstream: The sequence of bits resulting from an Ogg
      encapsulation of one or several logical bitstreams.  It consists
      of a sequence of pages from the logical bitstreams with the
      restriction that the pages of one logical bitstream MUST come in
      their correct temporal order.

   (Ogg) segment: The Ogg encapsulation process splits each packet into
      chunks of 255 bytes plus a last fractional chunk of less than 255
      bytes.  These chunks are called segments.
